---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


# OSMI

The `OSMI` project has been implemented for missing values imputation on expression data set. The advantage of the method is that it can be applied on a single subject DNA-methylation data. The method is based on the localisation of CpGs on chromosomes. Basically it replaces the missing values with its nearest available CpGs value.

## Installation instructions

OSMI can be installed using the following code:

```{r 'install', eval = FALSE}

pre-requisites

OSMi required this package to be available on insatllation
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
BiocManager::install("minfi")
BiocManager::install("impute")
BiocManager::install("methylclockData")
BiocManager::install("methylclock")
BiocManager::install("IlluminaHumanMethylation450kanno.ilmn12.hg19")

devtools::install_github("pdilena/methyLImp")
```

And the development version from [GitHub](https://github.com/Kemda-Imsid/OSMI) with:

```{r 'install_dev', eval = FALSE}
if (!require("remotes", quietly = TRUE)) install.packages("remotes")

remotes::install_github("Kemda-Imsid/OSMI")


library(devtools)
devtools::install_github("Kemda-Imsid/OSMI")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval = FALSE}
library("OSMI")
## basic example code
```


## Citation

Little by little, the bird makes its nest.

Please note that the `OSMI` was only made possible thanks to many other R and bioinformatics software authors, which are cited either in the vignettes and/or the paper(s) describing this package.

## Code of Conduct

Please note that the `OSMI` project is released with a [Contributor Code of Conduct](http://bioconductor.org/about/code-of-conduct/). By contributing to this project, you agree to abide by its terms.

## Development tools

* Continuous code testing is possible thanks to [GitHub actions](https://www.tidyverse.org/blog/2020/04/usethis-1-6-0/)  through `r BiocStyle::CRANpkg('usethis')`, `r BiocStyle::CRANpkg('remotes')`, and `r BiocStyle::CRANpkg('rcmdcheck')` customized to use [Bioconductor's docker containers](https://www.bioconductor.org/help/docker/) and `r BiocStyle::Biocpkg('BiocCheck')`.
* Code coverage assessment is possible thanks to [codecov](https://codecov.io/gh) and `r BiocStyle::CRANpkg('covr')`.
* The [documentation website](http://Kemda-Imsid.github.io/OSMI) is automatically updated thanks to `r BiocStyle::CRANpkg('pkgdown')`.
* The code is styled automatically thanks to `r BiocStyle::CRANpkg('styler')`.
* The documentation is formatted thanks to `r BiocStyle::CRANpkg('devtools')` and `r BiocStyle::CRANpkg('roxygen2')`.

For more details, check the `dev` directory.

This package was developed using `r BiocStyle::Biocpkg('biocthis')`.


